\documentclass[10pt, oneside]{article}
\usepackage{geometry}
\usepackage{color,pxfonts,fix-cm}
\usepackage[T1]{fontenc}
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
	
\usepackage{amssymb}
\usepackage{fancyhdr}

\usepackage{enumitem}
\setlist[enumerate]{nosep}
\setlist[itemize]{nosep}

\usepackage[hidelinks]{hyperref}

\usepackage{tocloft}
\renewcommand{\cfttoctitlefont}{\hfill\Large}
\renewcommand{\cftaftertoctitle}{\hfill}
\renewcommand{\cftsecnumwidth}{7em}
\renewcommand{\cftsubsecnumwidth}{6em}
\setcounter{tocdepth}{2}

\usepackage{titlesec}
\renewcommand{\thesection}{ARTICLE \Roman{section}}
\titleformat{\section}{\normalfont\Large\centering}{\thesection}{0.5em}{}
\renewcommand{\thesubsection}{SECTION \arabic{subsection}}
\titleformat{\subsection}[runin]{\normalfont\large\bfseries}{\thesubsection}{0.5em}{}
\renewcommand{\thesubsubsection}{\arabic{subsection}.\arabic{subsubsection}}
\titleformat{\subsubsection}[runin]{\normalfont\normalsize\itshape}{\thesubsubsection}{0.5em}{}


\title{Chapter Operations Manual \\ Beta TEST Chapter \\ IEEE-Eta Kappa Nu Association \\~\\ Established: 1906}
\author{\\Revision 2.5}
\date{}

\begin{document}

\pagestyle{fancy}
\fancyhead[R]{}
\renewcommand{\sectionmark}[1]{\markright{\MakeUppercase{\thesection. \ #1}}{}}
\renewcommand{\subsectionmark}[1]{}


\maketitle
\thispagestyle{empty}
\clearpage
\setcounter{page}{1}

\tableofcontents
\clearpage

\section{Chapter Charter}
\subsection{Name}
The name of this chapter shall be Beta Chapter of IEEE-Eta Kappa Nu Association.
\subsection{Location}
This chapter shall be located at Purdue University, West Lafayette, IN.

\section{Chapter Operations Manual}
\subsection{Governance}
This Chapter Operations Manual shall be the official governing document of Beta Chapter of IEEE-Eta Kappa Nu. This Operations Manual is subordinate to the IEEE-Eta Kappa Nu Operations Manual and future changes in those documents. The most recent version of these documents are available electronically from the IEEE-HKN web site http://www.hkn.org.
\subsection{Approval}
The original Chapter Operations Manual must be approved by a 2/3 majority vote of all student chapter charter members, any required university organizations, and the IEEE-Eta Kappa Nu Board of Governors.
\subsection{Amendments}
Amendments to this Chapter Operations Manual must be approved by a 2/3 majority vote of all student chapter charter members, the Student Activities and Organizations (SAO) office and any other required university organizations, and the IEEE-Eta Kappa Nu Board of Governors.

\section{Chapter Objectives}
\subsection{Uphold}
To uphold the purposes and ideals of IEEE-Eta Kappa Nu as set forth in the IEEE-Eta Kappa Nu Operations Manual.
\subsection{Promote}
To promote and encourage excellence in electrical and computer engineering fields of interest for the betterment of fellow students, the university, and the public at large.
\subsection{Foster}
To foster a spirit of respect and cooperation with the faculty of the Purdue University.
\subsection{Cooperate}
To cooperate with organizations such as:
\begin{enumerate}[label=\alph*.]
\item Local IEEE student branch
\item Other honor societies on campus
\item Other chapters of IEEE-Eta Kappa Nu
\end{enumerate}

\section{Chapter Emblem, Colors, \& Insignia}
The official emblem, colors, insignia, and publication of IEEE-Eta Kappa Nu are detailed in the IEEE-Eta Kappa Nu Operations Manual.

\section{Chapter Records \& Trustees}
\subsection{Records}
The records of Beta Chapter, including chapter correspondence, membership signature book, financial records, checkbooks, chapter meeting minutes and other records deemed important, shall be located at Purdue University.
\subsection{Faculty Advisor}
A Faculty Advisor shall serve as a liaison between the Chapter and the university. The requirements and responsibilities of the Faculty Advisor are detailed in the IEEE-Eta Kappa Nu Operations Manual.
\subsection{Trustees}
A Trustees Committee shall be appointed by the school official who signed the chapter petition. The Trustees Committee shall be chaired by the Faculty Advisor. Should the chapter become inactive, the trustee committee shall:
\begin{enumerate}[label=\alph*.]
\item Be custodian of all funds, records, and paraphernalia of the chapter.
\item Have full power to act and vote for the chapter during the period of inactivity
exactly as if the chapter was in active participation.
\item Have full power, with the approval of the IEEE-Eta Kappa Nu Executive
Director, to reorganize and reactivate the chapter when it deems the time is appropriate.
\end{enumerate}
\subsection{Digital Communications}
Management of any chapter digital communications media shall only be performed by current chapter officers, or their duly appointed designee, and primary management permissions will be passed to the current facilities director at each election.

\section{Eligibility \& Qualification}
\subsection{Who}
Undergraduate students, graduate students, and meritorious professionals such as faculty or distinguished alumni are eligible for induction IEEE-Eta Kappa Nu. The requirements for induction are detailed in the IEEE-Eta Kappa Nu Operations Manual.
\subsection{Minimum Hours}
Undergraduate candidates must have completed 9 hours of electrical or computer engineering courses, with a grade of C or better in each ECE class taken.
\subsection{Failures}
No candidate shall be considered for membership if they have on their record two failures in any of the electrical or computer engineering courses.
\subsection{Non-discrimination}
Membership and participation are free from dis- crimination on the basis of race, religion, color, sex, age, national origin or ancestry, genetic information, marital status, parental status, sexual orientation, gender identity and expression, disability, status as a veteran, or any other legally protected status.

\section{Induction}
\subsection{Orientation}
Eligible candidates shall be invited to attend an orientation reception. The purpose of the reception is to acquaint the prospective candidates with IEEE-Eta Kappa Nu, requirements for membership, and the current members with the prospective members.
\subsection{Candidate Tasks}
The candidates shall complete the following tasks prior to being eligible for election to initiate status.
\begin{itemize}
\item Two hours of ECE service coordinated by the Chapter
\item Two hours of community service coordinated by the Chapter
\item Two hours of service benefiting the Chapter
\item Two Person on Duty (POD) shifts in the Chapter lounge with at least one opening
or one closing shift
\item Introduce themselves and talk with the faculty advisers of the Chapter
\item Introduce themselves and talk with the Head of the Purdue University Electrical
and Computer Engineering Department
\item Introduce themselves and talk with at least three members of the Purdue University
Electrical and Computer Engineering Department faculty and/or lab staff. This may include at most one member of the lab staff; not including the Chapter advisers and Head of the Purdue University Electrical and Computer Engineering Department
\item Submit a resume to the Chapter
\end{itemize}
\subsection{Basis}
Eligible students shall be elected to initiate status on the basis of the
following three considerations:
\begin{enumerate}[label=\alph*.]
\item Compliance with the eligibility requirements in ARTICLE VI.
\item Extra-curricular activities and/or outside work.
\item Personality and character.
\end{enumerate}
(Reference www.hkn.org for suggested activities for inviting students to membership, possible initiation activities, and additional procedures to encourage candidates to accept this invitation to membership.)
\subsection{Notification}
Candidates shall be notified of their election individually by postal mail or electronic mail within 48 hours after the election. All letters shall be mailed simultaneously.
\subsection{Acceptance}
All who accept the invitation to membership shall be notified of the induction date, time, place, dress code, and procedures for the induction.
\subsection{Registration with Nationals}
Names and contact information for all candidates to be inducted shall be sent to IEEE-Eta Kappa Nu headquarters a minimum of three weeks prior to the induction date to enable membership certificates to be prepared for the initiation ceremony.
\\ (MEMBERSHIP IN IEEE-Eta Kappa Nu IS ONLY VALID WHEN INDUCTION FEES HAVE BEEN RECEIVED AND RECORDED BY HEADQUARTERS STAFF AND ALL ACCURATE INDIVIDUAL INFORMATION HAS BEEN ENTERED IN THE IEEE-Eta Kappa Nu DATABASE.)
\subsection{Ceremony} The formal induction shall proceed according to the Induction Ritual shown on the IEEE-Eta Kappa Nu website. To be inducted into IEEE-Eta Kappa Nu, an inductee MUST attend an induction ceremony. IEEE-Eta Kappa Nu head- quarters must be notified of inductees whose fees and information have been paid and recorded but who fail to attend the induction ceremony.

\section{Active Membership}
\subsection{Definition}
An Active Member shall be a member whom abides by these Bylaws and fulfills the requirements of active membership.
\subsection{Requirements}
An Active Member shall fulfill the following requirements:
\begin{itemize}
\item Have not missed two unexcused consecutive meetings
\item Serve at least one weekly POD shift during the semester
\item Serve either another weekly POD shift or with the approval of the Executive Committee a weekly hour of ECE or community service. Executive Committee members shall be exempt from this requirement.
\item Serve on at least one committee with an exception of currently elected officers
\item Complete two hours of community service per semester
\item Complete two hours of ECE service per semester
\item Maintain an updated resume with the Chapter
\end{itemize}

\section{Chapter Officers}
\subsection{Duration}
Chapter officers shall be elected once every semester. All newly elected officers shall take office at the conclusion of the last chapter meeting for the semester, or year, except for the President-Elect, who shall take office immediately following their election. The President-Elect will accede to the role of President at the conclusion of the last chapter meeting for the semester, or year..  All outgoing officers shall transfer their files and explain the duties of the office to the incoming officers at or before the last meeting of the semester. 
\subsection{Eligibility}
In order to be elected to an officer position nominee must be a currently active member of the Chapter. In order to be elected to the following officer position, the nominee must have satisfied all active member requirements for one complete semester:
\begin{itemize}
\item Treasurer
\end{itemize}
Additionally, in order to be elected to the following officer positions, the nominee
must have previously served a full duration in an officer position:
\begin{itemize}
\item President
\item Vice President
\end{itemize}
In order to be elected to the following officer position, the nominee must currently serve in an officer position:
\begin{itemize}
\item President-Elect
\end{itemize}
\subsection{Nominations}
Nominations shall be conducted at the regular meeting preceding the regular meeting in which elections shall take place. Following the nominations meeting one week shall be allowed for further nominations. At the end of the one week interval the official ballot shall be made available to the Chapter (one week before the election meeting).
\subsection{Elections}
Elections are to be held to allow sufficient time to ensure a smooth transition of officers. The method for elections shall be instant runoff voting by a single ballot for all officer positions. Elected nominees may only accept one position. Elections shall take effect at the end of the semester in which they are conducted.
\\~\\
The President will decide whether they intend to run for re-election for the next term by the eighth week of the current semester. If the President chooses to run for the following term, the election will take place as described for all other officer positions. If the President chooses not to run for the following term, a President-Elect election will be held during the 5th Active Member Meeting. If a President-Elect is elected, they will assume the role of the President in the following term.
\\~\\
A subsequent runoff election will take place if:
\begin{enumerate}[label=\alph*.]
\item A candidate has dropped the election, leaving the position empty.
\item There is a tie in the election results, and neither candidates are willing to drop after results have
been released.
\end{enumerate}
A subsequent runoff election will take place ideally the week after election week if not sooner. If such a position is empty (no candidates are running), a candidate will be nominated by the exec committee and given the option to accept. This candidate will be nominated based on previous societal engagement (Betabit points, active/pledge awards etc.). Eligibility for the position remain (See Article IX Section 2).
\subsection{Vacancy}
Any vacancy in the chapter offices shall be filled at the first regular meeting after the vacancy occurs or, when possible, before the vacancy occurs.
\subsection{Required Officers}
The required officers and their duties are detailed in the IEEE-Eta Kappa Nu Operations Manual. The positions of Corresponding Secretary and News Correspondent shall be merged into the single office of Public Relations Director.
\subsection{Chapter Specific Officers}
The chapter specific officers shall be:
\begin{enumerate}[label=\alph*.]
\item Events Director
\item Facilities Director
\item Operations Director
\item Recruitment Director
\item Volunteer Director
\item Lab Director
\item President-Elect
\end{enumerate}
\subsection{Officer Duties}
The duties of the Chapter officers shall be defined as follows.
\subsubsection{President}
The duties of the President shall be to:
\begin{itemize}
\item Supervise the affairs of the chapter
\item Preside and enforce decorum at all meetings of the chapter
\item Serve as the face of the chapter when interfacing with other organizations
\item Complete the annual chapter report
\item Attend the national student leadership conference during their term or
appoint arepresentative in their stead if unable to attend
\end{itemize}
\subsubsection{Vice President}
The duties of the Vice President shall be to:
\begin{itemize}
\item Oversee the Audit Committee, Fundraising, ECE outreach Committee, and Electric Vehicle Committee chairs
\item Oversee any other committee chairs without an overseeing officer
\item Attend the national student leadership conference during their term or
appoint a representative in their stead if unable to attend
\end{itemize}
\subsubsection{Recording Secretary}
The duties of the Recording Secretary shall be to:
\begin{itemize}
\item Keep record of all meetings of the Chapter
\item Disseminate the meeting minutes within 24 hours of the meeting
\item Issue notices of all special meetings of the Chapter
\item Keep a record of the current active members
\item Oversee the Antiquarian Committee chair
\end{itemize}
\subsubsection{Public Relations Director}
The duties of the Public Relations Director shall be to:
\begin{itemize}
\item Coordinate for all correspondence of the Chapter, except that related to the offices of the Treasurer and Events Director
\item Submit reports of the Chapter’s activities to the IEEE-HKN-BOG
\item Perform any duties related to THE BRIDGE and IEEE-HKN website
\item Handle any publicity for the Chapter
\item Correspond with the Purdue University Electrical and Computer Engineering Department
\item Oversee the Newsletter Committee chair
\end{itemize}
\subsubsection{Treasurer}
The duties of the Treasurer shall be to:
\begin{itemize}
\item Collect dues
\item Keeps accounts, deposits the organization’s funds, and makes expenditures in a manner approved by the Business Office for Student Organizations (BOSO)
\item Enforce the budget
\item Chair the Accounting Committee
\end{itemize}
\subsubsection{Events Director}
The duties of the Events Director shall be to:
\begin{itemize}
\item Submit all correspondence with the Purdue University office of Student Activities and Organizations
\item Chair the Events Committee
\end{itemize}
\subsubsection{Facilities Director}
The duties of the Facilities Director shall be to:
\begin{itemize}
\item Coordinate with the Electrical Engineering Building Deputy and Facilities Manager
\item Chair the Maintenance Committee
\item Oversee the Information Technology Committee chairs
\end{itemize}
\subsubsection{Operations Director}
The duties of the Operations Director shall be to:
\begin{itemize}
\item Chair the Lounge Committee
\end{itemize}
\subsubsection{Recruitment Director}
The duties of the Recruitment Director shall be to:
\begin{itemize}
\item Submit all new member information to Eta Kappa Nu Nationals
\item Chair the Initiation Committee
\end{itemize}
\subsubsection{Volunteer Director}
The duties of the Volunteer Director shall be to:
\begin{itemize}
\item Chair the Community Service Committee
\item Chair the ECE Service Committee
\end{itemize}
\subsubsection{Lab Director}
The duties of the Lab Director shall be to:
\begin{itemize}
\item Chair the Lab Committee
\end{itemize}
\subsubsection{President-Elect}
The duties of the President-Elect shall be to:
\begin{itemize}
\item Observe and learn from the President in all duties, including meetings and communications
\item Understand the responsibilities of the President before formal transition to the role
\end{itemize}

\section{Faculty Advisor(s)}
A Faculty Advisor shall serve as a liaison between the Chapter and the university. The requirements and responsibilities of the Faculty Advisor are detailed in the IEEE-Eta Kappa Nu Operations Manual.

\section{Executive Committee}
\subsection{Composition}
The executive committee shall consist of the officers defined in ARTICLE IX, SECTION 6 \& SECTION 7 and the Faculty Advisor(s).
\subsection{Power}
The executive committee shall have the power to make decisions affecting the day-to-day operation of the chapter between regularly scheduled chapter meetings.
\subsection{Purpose}
The executive committee shall serve as a planning committee for activities throughout the semester and shall propose the initial agendas for the regular or special chapter meetings.
\subsection{Quorum}
A quorum for transaction of business at an executive committee meeting shall be a majority of the executive committee members.
\subsection{Faculty Advisor}
The Faculty Advisor(s) must be invited to all executive committee meetings, but is not required to attend.
\subsection{Expenditures}
The executive committee shall be authorized to make expenditures of USD 200 or less for goods and services necessary for the operation of the chapter without a vote of the entire membership
\subsection{Finality}
Decisions of the executive committee may be overturned by a majority vote of the chapter.
\subsection{Meetings}
The executive committee shall meet before each regular and special meeting of the chapter, and additionally at least one semester planning meeting before the end of the first week of the semester.
\subsection{Chair}
The President of the chapter shall preside as the chair of the executive committee.

\section{Committees}
\subsection{Creation}
In addition to the standing committees specified below, the chapter president shall appoint such other committees as he or she deems necessary with the approval of the executive committee, or as deemed necessary, by the chapter.
\subsection{Membership}
Committee membership shall be on a volunteer basis by chapter members. Committee membership eligibility shall be approved by the executive committee.
\subsection{Appointment}
The president may appoint individuals to serve on any committee. Committee chairs shall:
\begin{enumerate}[label=\alph*.]
\item Be elected by the chapter members OR
\item Be appointed by the chapter president OR
\item Be elected by committee members
\end{enumerate}
\subsection{Standing Committees}
The Standing Committees shall be:
\begin{enumerate}[label=\alph*.]
\item Accounting Committee
\item Antiquarian Committee
\item Auditing Committee
\item Community Service Committee
\item Events Committee
\item ECE Outreach Committee
\item ECE Service Committee
\item Electric Vehicle Committee
\item Fundraising Committee
\item Information Technology Committee
\item Lab Committee
\item Lounge Committee
\item Maintenance Committee
\item News Committee
\item Initiation Committee
\end{enumerate}
\subsection{Duties}
The duties of the Standing Committees shall be defined as follows.
\subsubsection{Accounting Committee}
The duties of the Accounting Committee shall be to:
\begin{itemize}
\item Cycle the lounge cash fund on a daily basis
\item Assist with management of the Chapter’s funds and accounts
\end{itemize}
\subsubsection{Antiquarian Committee}
The duties of the Antiquarian Committee shall be to:
\begin{itemize}
\item Chronicle the Chapter’s activities
\item Maintain the Chapter’s archives
\end{itemize}
\subsubsection{Auditing Committee}
The duties of the Auditing Committee shall be to:
\begin{itemize}
\item Perform monthly audit of the Chapter’s accounts
\item Perform the end of semester audit of the Chapter’s accounts
\end{itemize}
\subsubsection{Community Service Committee}
The duties of the Community Service Committee shall be to:
\begin{itemize}
\item Plan \& Coordinate all community service activities for the Chapter
\item Schedule a minimum of eight activities for the semester
\end{itemize}
\subsubsection{Events Committee}
The duties of the Events Committee shall be to:
\begin{itemize}
\item Plan \& Coordinate all social activities for the Chapter
\item Plan \& Coordinate a semester banquet for the Chapter
\item Plan \& Coordinate a semester picnic
\item Schedule a minimum of twelve activities for the semester
\end{itemize}
\subsubsection{ECE Outreach Committee}
The duties of the ECE Outreach Committee shall be to:
\begin{itemize}
\item Plan \& Coordinate all ECE outreach events
\item Schedule a minimum of one educational outreach event for the semester
\item Support Purdue University Electrical and Computer Engineering outreach events
\end{itemize}
\subsubsection{ECE Service Committee}
The duties of the ECE Service Committee shall be to:
\begin{itemize}
\item Plan \& Coordinate all ECE service activities for the benefit of the students
\item Schedule a minimum of eight activities for the semester
\end{itemize}
\subsubsection{Electric Vehicle Committee}
The duties of the Electric Vehicle Committee shall be to:
\begin{itemize}
\item Maintain the Chapter’s entry in the evGrandprix
\item Race the entry in the annual evGrandprix
\end{itemize}
\subsubsection{Fundraising Committee Committee}
The duties of the Fundraising Committee Committee shall be to:
\begin{itemize}
\item Acquire and coordinate industry sponsorship
\item Coordinate donations to the Chapter
\end{itemize}
\subsubsection{Information Technology Committee}
The duties of the Information Technology Committee shall be to:
\begin{itemize}
\item Maintain physical information infrastructure
\item Maintain the Chapter’s website infrastructure
\item Maintain a standard operating procedure wiki
\item Maintain the information infrastructure required for the operation of the
Chapter’s lounge
\end{itemize}
\subsubsection{Lab Committee}
The duties of the Lab Committee shall be to:
\begin{itemize}
\item Maintain a student lab space sponsored by the Chapter
\item Coordinate use of the student lab space
\end{itemize}
\subsubsection{Lounge Committee}
The duties of the Lounge Committee shall be to:
\begin{itemize}
\item Coordinate operations of the Chapter’s lounge
\item Order \& restock inventory
\item Perform inventory checks every two weeks during the semester
\end{itemize}
\subsubsection{Maintenance Committee}
The duties of the Maintenance Committee shall be to:
\begin{itemize}
\item Maintain the physical infrastructure and equipment for the Chapter’s lounge
\item Maintain the physical infrastructure and equipment for the Chapter sponsored
labspace
\end{itemize}
\subsubsection{News Committee}
The duties of the News Committee shall be to:
\begin{itemize}
\item Publish a chapter newsletter every semester
\item Submit articles to THE BRIDGE during the semester
\end{itemize}
\subsubsection{Initiation Committee}
The duties of the Initiation Committee shall be to:
\begin{itemize}
\item Obtain list of eligible initiate candidates
\item Coordinate interviews of the initiate candidates
\item Oversee and track the Chapter’s initiation process
\item Coordinate induction of initiates
\end{itemize}

\section{Chapter Meetings}
\subsection{Quorum}
A quorum for the legal transaction of chapter business shall consist of at least 50\% of the active members of the chapter. Student members pursuing a cooperative program or those who are off the campus on an industrial assignment at the time of a meeting shall not be counted in the total membership for the purpose of deter - mining a quorum. In addition, active members with approved, full-semester conflicts with chapter meetings, as acknowledged by the executive committee, are likewise not counted in the total membership for the purpose of determining quorum.
\subsection{Absences}
All absences from meetings by members of the Chapter shall be unexcused unless approved by the Executive Committee. All excused absences shall be presented at the Chapter meeting with the reason for the absence.
\subsection{Minimum Meetings}
A minimum of eight regular meetings shall beheld each semester according to a schedule published at the beginning of the semester.
\subsection{Special Meetings}
The chapter president may call a special meeting at any time and shall be required to call a special meeting within two weeks upon request of five active members or the faculty adviser.
\subsection{Rules}
The rules governing this organization for conducting business shall be, in order of precedence:
\begin{enumerate}[label=\alph*.]
\item The IEEE-Eta Kappa Nu Operations Manual
\item This Operations Manual
\item The latest version of Robert’s Rules of Order.
\end{enumerate}
\subsection{Suffrage}
Only active members may vote on Chapter matters.
\subsection{Questions of Order}
Except as provided in this Operations Manual, all questions of order shall be decided by the Executive Committee.
\subsection{Order of Business}
The order of a general business meeting shall be as follows:
\begin{enumerate}[label=\alph*.]
\item Roll Call
\item Reading of the previous meeting’s minutes
\item Officer Reports
\item Committee Reports
\item Old Business
\item New Business
\item Election of Officers (if on agenda)
\item Election of New members (if on agenda)
\item Appointment of Committees (if needed)
\item Special Papers and Presentations
\item Announcements, Discussion
\end{enumerate}

\section{Dues, Fees, \& Assessments}
\subsection{National Fee}
The induction fee shall be determined by the IEEE-Eta Kappa Nu Board of Governors and reported by IEEE-Eta Kappa Nu Headquarters.
\subsection{Local Fee}
A local induction fee may be accessed by the chapter. This fee shall be equal to the local fee during the previous semester, unless the chapter has voted for a change in fees.
\subsection{Waiver of Fees}
The Chapter’s Executive Committee, at their discretion, can waive an individual’s fees with just cause. The Treasurer shall be instructed to pay the Association’s fee from chapter funds.

\section{Chapter Funds}
\subsection{General Fund}
There shall be a General Fund consisting of local chapter dues, fees, assessments, bank interest, and proceeds collected from other chapter activities.The general fund shall be used to pay all operating expenses of the chapter.
\subsection{Deposits}
Monies shall be deposited in an account approved by the university and the officers of the Chapter.
\subsection{Account Name}
The name on the account shall be Beta Chapter of IEEE- Eta Kappa Nu.
\subsection{Administration}
The Treasurer shall establish and administer the General Fund and all accounts. The Treasurer shall have the authority to open accounts and to deposit funds.
\subsection{Other Accounts}
Multiple accounts may be opened to separate funds from various chapter programs.
\subsection{Disbursement}
Disbursements from any chapter account shall be approved by the chapter members or may be approved by the executive committee if under USD 200. All disbursements require at least two signatures.
\subsection{Financial Reports}
The treasurer shall prepare a financial report for each regular meeting of the chapter. The financial report shall include current balances, reports of deposits and expenditures since the last meeting, and an estimate of upcoming deposits and expenditures. The treasurer shall keep books open to inspection by any member of the Chapter during a regularly scheduled meeting.
\subsection{Audit}
The newly elected treasurer and one other member appointed by the president shall perform an audit of the treasurer’s books at the end of the treasurer’s term.
\subsection{Tax ID}
For bank accounts that require a Tax ID number, the Tax ID number for Beta Chapter shall be used. This Tax ID number shall be determined by the Chapter and the Purdue University Business Office for Student Organizations. Chapter accounts shall not be established in any member’s name, nor should the social security number of any member or faculty adviser be used on chapter accounts.
\subsection{Fiscal Year}
The fiscal year for reporting revenue and expenses shall be July 1 through June 30.
\subsection{Budget}
A Budget shall be required for each semester. Funds allocated via the budget shall not require further approval by the chapter upon ratification of the budget. The ratification of the budget is to be through a majority vote of the chapter.

\section{Honors}
\subsection{Graduate Honors}
Upon graduation, having completed at least one semester of active membership in the Chapter, active members are entitled to receive a paddle and a stole. The cost of the paddle and stole shall be covered for one graduation. Upon additional graduations, graduates are eligible to purchase a paddle and a stole from the Chapter at their own expense.
\subsection{Officer Honors}
Upon completion of a full duration of service, Chapter officers shall receive a lapel pin. In addition, the President shall receive a gavel and theVice President shall receive a pen.
\subsection{Chapter Honors}
All chapter Honors unless otherwise stated in the Bylaws shall be presented in the form of a plaque or a medal.

\clearpage

{\normalfont\Large \centering Approvals: \\~\\}

\noindent The above Chapter Operations Manual was approved by the members of the Beta
Chapter at a [regular/special] business meeting held on \rule{4cm}{0.4pt}, with \rule{1cm}{0.4pt} members present and was approved by a vote of \rule{1cm}{0.4pt} in favor and \rule{1cm}{0.4pt} opposed. This Operations Manual shall become effective on \rule{4cm}{0.4pt}.
\\[2\baselineskip]

\noindent \rule{8cm}{0.4pt} \hfill {\rule{4cm}{0.4pt} \\
\noindent Chapter President \hfill Date
\\[2\baselineskip]
\noindent \rule{8cm}{0.4pt} \hfill {\rule{4cm}{0.4pt} \\
\noindent Faculty Advisor \hfill Date
\\[2\baselineskip]
\noindent \rule{8cm}{0.4pt} \hfill {\rule{4cm}{0.4pt} \\
\noindent Student Activities and Organizations Office \hfill Date
\\[2\baselineskip]

\noindent Approval by the IEEE-Eta Kappa Nu Board of Governors and Executive Director:
\\[2\baselineskip]
\noindent \rule{8cm}{0.4pt} \hfill {\rule{4cm}{0.4pt} \\
\noindent President \hfill Date
\\[2\baselineskip]
\noindent \rule{8cm}{0.4pt} \hfill {\rule{4cm}{0.4pt} \\
\noindent Vice President \hfill Date
\\[2\baselineskip]
\noindent \rule{8cm}{0.4pt} \hfill {\rule{4cm}{0.4pt} \\
\noindent Past President \hfill Date
\\[2\baselineskip]
\noindent \rule{8cm}{0.4pt}  \hfill {\rule{4cm}{0.4pt} \\
\noindent Executive Director \hfill Date \\

\fancyhead{}

\end{document}
